---
title: "Case Study"
author: "Austin Hsin"
date: "2023-10-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Airbnb
```{r}
library(p8105.datasets)
data(nyc_airbnb)

str(nyc_airbnb)

nyc_airbnb |>
  count(room_type)

nyc_airbnb |>
  count(neighbourhood_group)
```

# Brainstorm questions

- Where are AirBNBs expensive?
  - Borough? Neighborhood?
  - Do other factors (room type) affect price? What about rating?
- How long are AirBNBs active?
  - Are AirBNBs illegal and do they get shut down?
- Which units have the most availability?
- How is review score impacted by location?
- How many apts are run by one host?
  - Does that affect price?
  - Does that vary by neighborhood? 
- Where are AirBNBs? 
  - Borough? Neighborhood?
  - Lat and long?


## Do some EDA

```{r}
nyc_airbnb |> 
  count(borough)
```

```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(mean_price = mean(price)) |> 
  pivot_wider(
    names_from = room_type, 
    values_from = mean_price
  )
```


```{r}
nyc_airbnb |> 
  group_by(borough, room_type) |> 
  summarize(median_price = median(price)) |> 
  pivot_wider(
    names_from = room_type, 
    values_from = median_price
  )
```

```{r}
nyc_airbnb |> 
  ggplot(aes(x = price)) + 
  geom_histogram() + 
  facet_grid(borough ~ room_type)
```

```{r}
nyc_airbnb |> 
  filter(price >= 9500)
```

```{r}
nyc_airbnb |> 
  filter(price < 1000, room_type == "Entire home/apt") |> 
  ggplot(aes(x = price)) + 
  geom_histogram() + 
  facet_grid(. ~ borough)
```


```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  group_by(neighbourhood) |> 
  summarize(
    n_apt = n(),
    mean_price = mean(price)) |> 
  arrange((mean_price))
```

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) |> 
  ggplot(aes(x = price, y = neighbourhood)) + 
  geom_density_ridges()
```

## Try to make a map

```{r}
nyc_airbnb |> 
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  ggplot(aes(x = lat, y = long, color = price)) + 
  geom_point()
```


Try something else entirely.

```{r}
nyc_airbnb |>  
  filter(
    price < 1000, 
    room_type == "Entire home/apt", 
    borough == "Manhattan") |> 
  sample_n(500) |> 
  leaflet() |> 
  addProviderTiles(providers$CartoDB.Positron) |> 
  addCircleMarkers(~lat, ~long, radius = .5)
```
